Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-10 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
fixing an acronym

As a volunteer based system, there are some issues worth 
noting \cite{sarmenta2001volunteer,web:BOINC} :\begin{enumerate}
\item Volunteers are anonymous, only the IP address sent in 
each request is known.
\item As anonymous entities, volunteers are not accountable. 
If a volunteer misbehaves in some way the provider cannot 
prosecute or discipline the volunteer. In the case of JavaScript,
this issue is aggravated because even if it is obfuscated, source code
and data is sent to clients. 
\item Participants must also trust the application provider, 
regarding invasion of privacy, the integrity of their devices, 
and intended application. 
\end{enumerate}

@@

A summary of the results of each run is also shown in Table
\ref{tab:summary:os}, which shows the median number of Internet Protocol addresses (IPs)
intervening in each experiment,  median time needed
to finish the experiment, median number of HTTP {\tt PUT}s per IP, and
then two columns showing the percentage of experiments that took less
than the two baseline experiments shown in the introduction to this
section. The first striking result is that in all cases, 50\% of the
experiments involved 5 or less IPs. This is consistent with results
previously obtained \cite{DBLP:conf/gecco/GuervosG15} which found 6 to be
the usual number of IPs that participated in an experiment. The
maximum number of different IPs for each experiment is also in the
same range and of the order of 10, which is also consistent with
prior work. The median time has a big range of variation, but 50\% of
the time takes less than several minutes, from around 4 minutes in the
best case to roughly 2/3 of an hour in the worst case. That figure is
not competitive, {\em a priori}, with the baseline experiment, that is
why it is interesting to look at the columns which measure
the percentage of experiments in which the solution was found in less
time than the baseline. It is similar in all three cases, with around
20\% on average for the first baseline experiment, roughly 3\% in the
second case. The comparison is not totally fair: this experiment takes
place in a browser, and in fact most of the time is devoted to
presenting the charts; the server is also not the same since it is run in a
PaaS instead of a high-performance desktop computer, and it is also a
remote server, not a local server as in the baseline experiment. But
even in this case, we were looking for creating a framework that
allowed us to run evolutionary computation experiments {\em faster} than
in our very own computer. And the results indicate that although it will
happen in 1 out of roughly 5 or roughly 20 cases, depending on what baseline
experiment you choose, it will not happen always or even most of
the time. One of the problems is shown in the last column, which
indicates the statistical correlation between the number of IPs
participating in one experiment and the next. In all cases,
correlation is so low as to affirm that there is almost no
relationship between them, that is, computing nodes are not {\em
  staying} after the solution has been found. This is a feature of
this implementation: the user has to actively reload the page to make
the evolutionary algorithm start again. Thus, the user can decide if to continue sharing resources or not. % (Paloma) Feature or disadvantage?
However, it puts a probably            % (Mario) Feature if you only want to share your CPU a little  
unnecessary upper limit on the time, or number of experiments, that a user
will voluntarily perform.

>>>>

As a volunteer based system, there are some issues worth 
noting \cite{sarmenta2001volunteer,web:BOINC} :\begin{enumerate}
\item Volunteers are anonymous, only the Internet Protocol addresses (IP) sent in 
each request is known.
\item As anonymous entities, volunteers are not accountable. 
If a volunteer misbehaves in some way the provider cannot 
prosecute or discipline the volunteer. In the case of JavaScript,
this issue is aggravated because even if it is obfuscated, source code
and data is sent to clients. 
\item Participants must also trust the application provider, 
regarding invasion of privacy, the integrity of their devices, 
and intended application. 
\end{enumerate}

@@

A summary of the results of each run is also shown in Table
\ref{tab:summary:os}, which shows the median number of IPs
intervening in each experiment,  median time needed
to finish the experiment, median number of HTTP {\tt PUT}s per IP, and
then two columns showing the percentage of experiments that took less
than the two baseline experiments shown in the introduction to this
section. The first striking result is that in all cases, 50\% of the
experiments involved 5 or less IPs. This is consistent with results
previously obtained \cite{DBLP:conf/gecco/GuervosG15} which found 6 to be
the usual number of IPs that participated in an experiment. The
maximum number of different IPs for each experiment is also in the
same range and of the order of 10, which is also consistent with
prior work. The median time has a big range of variation, but 50\% of
the time takes less than several minutes, from around 4 minutes in the
best case to roughly 2/3 of an hour in the worst case. That figure is
not competitive, {\em a priori}, with the baseline experiment, that is
why it is interesting to look at the columns which measure
the percentage of experiments in which the solution was found in less
time than the baseline. It is similar in all three cases, with around
20\% on average for the first baseline experiment, roughly 3\% in the
second case. The comparison is not totally fair: this experiment takes
place in a browser, and in fact most of the time is devoted to
presenting the charts; the server is also not the same since it is run in a
PaaS instead of a high-performance desktop computer, and it is also a
remote server, not a local server as in the baseline experiment. But
even in this case, we were looking for creating a framework that
allowed us to run evolutionary computation experiments {\em faster} than
in our very own computer. And the results indicate that although it will
happen in 1 out of roughly 5 or roughly 20 cases, depending on what baseline
experiment you choose, it will not happen always or even most of
the time. One of the problems is shown in the last column, which
indicates the statistical correlation between the number of IPs
participating in one experiment and the next. In all cases,
correlation is so low as to affirm that there is almost no
relationship between them, that is, computing nodes are not {\em
  staying} after the solution has been found. This is a feature of
this implementation: the user has to actively reload the page to make
the evolutionary algorithm start again. Thus, the user can decide if to continue sharing resources or not. % (Paloma) Feature or disadvantage?
However, it puts a probably            % (Mario) Feature if you only want to share your CPU a little  
unnecessary upper limit on the time, or number of experiments, that a user
will voluntarily perform.
